manuscript_analysis_clean

### 2021-08-08 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd
Updated outlier removal function for by trial RT data again. Outliers were already removed from the data. The function is not necessary but still kept in the script to double check outliers.

    if (length(part_id) != 0) {
    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }

>>>>

    if (length(which(rt_trial$id %in% part_id & rt_trial$task == taskName)) != 0) {
    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }
